A Simple Minibatch Acceptance Test for MCMC

### 2016-05-17 nips_2016.tex
keep writing experiments

We use this experiment to illustarte another property of our mini-batch MH testing:

{\color{blue}
Daniel: TODO
Add the roofline description.

@@

\subsection{Neural Network Optimization}\label{ssec:nets}

\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will hopefully show results for neural networks on BIDMach.}
\end{figure}

>>>>

We use this experiment to illustarte another property of our mini-batch MH testing: when the size of mini-batch increase to a threshold, the accuracy / loglikelihood of sampled data at a fix iteration number will not improve with larger mini-batch size, see Fig.~4c. This is because the variance of $\Delta'$ decrease with large mini-batch, and the error of our mini-batch MH testing is proportional to our estimation error of variance of $\Delta'$. When the $var(\Delta')$ decrease to a threshold, the error of our mini-batch MH testing can be ignored.

{\color{blue}

@@

\subsection{Neural Network Optimization}\label{ssec:nets}
In this experiment, we apply about mini-batch MH testing with SGHMC proposer to sample the parameter instances from 
\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will hopefully show results for neural networks on BIDMach.}
\end{figure}
